---
title: "Group_20_TP1"
author: "Sean Pedersen, Brooke Ealey, Stanley Yuan, Cole Smith"
date: "3/27/2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## We use the ROCR package to produce ROC curves on the predictions from the test subset. The e1071 package is used to call the svm() function.

```{r}

rm(list=ls())
installIfAbsentAndLoad <- function(neededVector) {
  for(thispackage in neededVector) {
    if( ! require(thispackage, character.only = T) )
    { install.packages(thispackage)}
    require(thispackage, character.only = T)
  }
}

needed <- c('e1071','ROCR')  
installIfAbsentAndLoad(needed)
```

#### Preload data
```{r}
set.seed(1)
x<-matrix(rnorm (200*2) , ncol=2)
x[1:100,]<-x[1:100,]+2
x[101:150 ,]<-x[101:150,]-2
y<-c(rep(1,150) ,rep(2,50))
dat<-data.frame(x=x,y=as.factor(y))
train<-sample (200,100)
```

#### Function to plot ROC curve 
```{r}
rocplot <- function (pred , truth , ...){
  predob = prediction (pred , truth)
  perf = performance (predob , "tpr", "fpr")
  plot(perf ,...)
}
```

## Instead of getting the class labels, we can also get fitted values from svm() using decision.values = TRUE parameter

```{r}
svmfit.opt<- svm(y~ ., data=dat[train ,], kernel ="radial", gamma=2, cost=1, decision.values =T)
fitted <-attributes (predict (svmfit.opt ,dat[train ,], decision.values=TRUE))$decision.values
```

## We generate the ROC curve with the rocplot() function. We can also change the value of gamma and see if it improves our predictions.

```{r}
par(mfrow = c(1, 2))
rocplot(fitted, dat[train, "y"], main = "Training Data")

svmfit.flex <- svm(y ~ ., data = dat[train, ], kernel = "radial", gamma = 50, cost = 1, decision.values = TRUE)
fitted <- attributes(predict(svmfit.flex, dat[train, ], decision.values = T))$decision.values
rocplot(fitted, dat[train, "y"], add = T, col = "red")

```

```{r}
fitted <- attributes(predict(svmfit.opt, dat[-train, ], decision.values = T))$decision.values
rocplot(fitted, dat[-train, "y"], main = "Test Data")
fitted <- attributes(predict(svmfit.flex, dat[-train, ], decision.values = T))$decision.values
rocplot(fitted, dat[-train, "y"], add = T, col = "red")
```


