---
title: "Group_20_TP1"
author: "Sean Pedersen, Brooke Ealey, Stanley Yuan, Cole Smith"
date: "3/28/2020"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## We use the ROCR package to produce ROC curves on the predictions from the test subset. The e1071 package is used to call the svm() function
```{r}

rm(list=ls())
installIfAbsentAndLoad <- function(neededVector) {
  for(thispackage in neededVector) {
    if( ! require(thispackage, character.only = T) )
    { install.packages(thispackage)}
    require(thispackage, character.only = T)
  }
}

needed <- c('e1071','ROCR')  
installIfAbsentAndLoad(needed)
```

#### Preload data
```{r}
set.seed(1)
x<-matrix(rnorm (200*2) , ncol=2)
x[1:100,]<-x[1:100,]+2
x[101:150 ,]<-x[101:150,]-2
x <- rbind(x, matrix(rnorm(50 * 2), ncol = 2))
y<-c(rep(1,150) ,rep(2,50))
y <- c(y, rep(0, 50))
x[y == 0, 2] <- x[y == 0, 2] + 2
dat <- data.frame(x = x, y = as.factor(y))
```
## The plot below shows a data set with three distinct classes. The svm() function can also be used to classify observations from multiple clases 
```{r}
par(mfrow = c(1, 1))
plot(x, col = (y + 1))
```

## The svm() function now will perform multi-class classification since the dataset we generated now has three class labels.

```{r}
svmfit <- svm(y ~ ., data = dat, kernel = "radial", cost = 10, gamma = 1)
plot(svmfit, dat)
```

